Author disambiguation of large-scale semi-labeled collections of scientific articles

### 2015-08-20 paper.tex
save

In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual (without knowing who). Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge of pairs ${\cal C} = \{ (a, s) \in
{\cal A} \times {\cal S} \}$, each indicating that signature $s$ is known with high confidence
to belong to individual $a$. Equivalently, ${\cal C}$ can be seen as a set of partial
clusters $c_a$, each including all signatures $s$ for which $(s, a) \in {\cal C}$. \glnote{Change notations for ${\cal C}$!!}

@@

\textit{Building a training set.} The distinctive aspect of our work is the
knowledge of more than 1 million of crowdsourced annotations ${\cal C} = \{(a,
s) \in {\cal A} \times {\cal S}\}$, each indicating that signature $s$ is known
to correspond to individual $a$. In particular, this data can be used to
generate positive pairs $(x=(s_1, s_2), y=0)$ for all $(s_1, a_1)$, $(s_2, a_2)
\in {\cal C}$ such that $a_1=a_2$. Similarly, negative pairs $(x=(s_1, s_2), y=1)$
can be extracted for all $(s_1, a_1)$, $(s_2, a_2)
\in {\cal C}$ such that $a_1 \neq a_2$.

>>>>

In this
framework, author disambiguation can be stated as the problem of
finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
signatures belonging to the same individual $a_i$. Alternatively, the set
${\cal A}$ may remain (possibly partially) unknown, such that author
disambiguation boils down to finding a partition ${\cal C}$ where
subsets $c_i$  each corresponds to the set of all signatures from a same
individual (without knowing who). Finally, in the case of partially annotated databases as studied in
this work, the setting extends with the partial knowledge $\bar{{\cal C}} = \{ \bar{c_0}, ..., \bar{c_{M-1}} \}$ of ${\cal C}$,
such that $\bar{c_i} \subseteq c_i$, with $\bar{c_i}$ possibly empty.
Or put otherwise, the setting extends with the knowledge that all signatures
$s \in \bar{c_i}$ belong to author $a_i$.

@@

\textit{Building a training set.} The distinctive aspect of our work is the
knowledge of more than 1 million of crowdsourced annotations $\bar{\cal C} = \{
\bar{c_0}, ..., \bar{c_{M-1}} \}$, indicating together that all signature $s \in
\bar{c_i}$ are known to correspond to the same individual $a_i$. In particular,
this data can be used to generate positive pairs $(x=(s_1, s_2), y=0)$ for all
$s_1, s_2 \in \bar{c_i}$, for all $i$. Similarly, negative pairs $(x=(s_1,
s_2), y=1)$ can be extracted for all $s_1 \in \bar{c_i}, s_2 \in \bar{c_j}$, for
all $i \neq j$.
